---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countmissing

<!-- badges: start -->
<!-- badges: end -->

The goal of countmissing is to create a new data frame that summarizes the number of missing values for all columns in a given data set "data" per level of column "group". This provides a high level overview of the data set.

## Installation

You can install the development version of countmissing like so:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/assignment-b2-cynthiaachung", ref = "0.1.0")
```

## Usage

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column.

```{r example1}
library(countmissing)
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r example2}
airquality |> count_all_missing_by_group(Month) 
```
